### 2019-05-14 README.Rmd
binder working

This repository contains data files that have been derived from the raw eye-tracker data. The raw eye-gaze files are very large and so are not stored here. They can be found at: <https://osf.io/yrdzv/>.

@@

### How to download or install

You can download the compendium as a zip from from this URL: <https://github.com/danielpearson90/vmacfeaturesearch/archive/master.zip>

Once you have downloaded and extracted the compendium, you can open [the project](vmacfeaturesearch.Rproj) with RStudio, and knit [analysis_report.rmd](analysis/analysis_report.rmd) to produce a report containing all statistical analyses contained in our preprint. You can also knit [paper.Rmd](analysis/paper/paper.Rmd) to produce a reproducible copy of the preprint.

This compendium is still a work in progress, with Docker integration planned for the future.

>>>>

@@

### Contents
- [:file_folder: analysis](/analysis): Contains analysis report in R Markdown format, as well as R script format.
- [:file_folder: analysis/paper](/analysis/paper): R markdown source document for the manuscript.
- [:file_folder: analysis/data](/analysis/data): Data files that have been dericed from the raw eye-tracker data. The raw eye-gaze files are very large and so are not stored here. They can be found at: <https://osf.io/yrdzv/>.
- [:file_folder: analysis/figures](/analysis/figures): Figures generated in the analysis.

### Reproducibility
This repository is organized as a reproducible research compendium. 
Click the ![Binder](https://mybinder.org/badge_logo.svg) button above to explore in an interactive RStudio session (this takes approximate 15-20 mins to build). Binder uses [rocker-project.org](https://rocker-project.org) Docker images to ensure a consistent and reproducible computational environment.  These Docker images can also be used locally.

To explore the code locally, clone or download this repository into RStudio or your perferred environment and install the compendium by running `devtools::install(dep=TRUE)`.

This compendium is checked by Travis-CI continuous integration.  Click the ![Build Status](https://travis-ci.org/cboettig/noise-phenomena.svg?branch=master) button above for details.
